---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# teztaxr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

An R package to scrape transaction data from the Tezos blockchain and calculate statements and summaries useful for tax calculations.

**Disclaimer: This software has been written by the authors for personal use, and it is provided "as is," without warranty of any kind. Nothing in the documentation and no statement or summary generated by the software should be considered as tax advice. Please seek the advice of a qualified tax professional.**

## Installation

You can install the development version of teztaxr from [GitHub](https://github.com/datcsv/teztaxr) with:

``` r
devtools::install_github("datcsv/teztaxr")
```

## Example

Example usage:

```{r example, message = FALSE}
library(tidyverse)
library(teztaxr)

# look up all transactions by a given address during a specified time interval
address <- "tz1cnfEeha6cibgKVs6DTGKyrP9V4bz5F2N6"
span <- c("2022-01-01T00:00:00Z", "2022-03-31T23:59:59Z")
tzkt_operations(address, span = span) %>%
  select(type, timestamp, gasUsed, storageFee)

# look up transactions by hash
hash <- "onujxsRLwcYZuKVTKG1JLwFEe9EWBSPdiB6pRCg5WcH6NpXdRxA"
tzkt_operations_hash(hash) %>%
  select(type, timestamp, gasUsed, storageFee)
```

